\vspace{-2.75cm}Technological Change and U.S. Foreign Aid\vspace{-0.5cm}

### 2022-12-14 Paper.tex
update

\section*{Introduction}
The United States (U.S.) has been increasingly funding digital infrastructure in countries around the world.\footnote{All R code, data, and \LaTeX \;code can be found at  underlying my analysis can be found on GitHub at https://github.com/nnray.} Simultaneously, the People's Republic of China (China) has advanced its own digital infrastructure projects and financial assistance to become the ``lender of first resort'' for developing countries in the last decade \parencite[1]{dreher2022}. Available explanations do not sufficiently address this seeming great power competition along digital infrastructure. In this article I put forth an explanation specifying that the U.S. is funding digital infrastructure in Africa to prevent the Chinese from building such infrastructure and closing market access to U.S. technology firms.

>>>>

\section*{Introduction}
The United States (U.S.) has been increasingly funding digital infrastructure in countries around the world.\footnote{All R code, data, and \LaTeX \;code underlying my analysis can be found in the corresponding repository on GitHub at https://github.com/nnray.} Simultaneously, the People's Republic of China (China) has advanced its own digital infrastructure projects and financial assistance to become the ``lender of first resort'' for developing countries in the last decade \parencite[1]{dreher2022}. Available explanations do not sufficiently address this seeming great power competition along digital infrastructure. In this article I put forth an explanation specifying that the U.S. is funding digital infrastructure in Africa to prevent the Chinese from building such infrastructure and closing market access to U.S. technology firms.
